Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-06-29 vertical-thermal-review_SI.Rmd
small fix to SI
@teixeirak i added the citations here

# `r Notes_S1`: Biophysical drivers of $T_{leaf}$

@@

Micrometeorological data was downloaded for each site from NEON (neonUtilies R package) at 30 minute intervals for 2015-2020. To focus on the middle of the growing season, the data was constrained to be for the month of July each year. Per site, we calculated the mean maximum and minimum values of each variable by day and by sensor height. In Figure S1 we expanded on Figure `r fig_NEON_vertical` by including 22 sites representing five forest structure types.

>>>>

# Note `r Notes_leafTbiophysics`: Biophysical drivers of T~leaf~

@@

Micrometeorological data was downloaded for each site from NEON (neonUtilies R package) at 30 minute intervals for 2015-2020 [@https://doi.org/10.48443/77n6-eh42;  @https://doi.org/10.48443/0tyt-ky71;  @https://doi.org/10.48443/7rs6-ff56;  @https://doi.org/10.48443/8a01-0677;  @https://doi.org/10.48443/w9nf-k476]. To focus on the middle of the growing season, the data was constrained to be for the month of July each year. Per site, we calculated the mean maximum and minimum values of each variable by day and by sensor height. In Figure S1 we expanded on Figure `r fig_NEON_vertical` by including 22 sites representing five forest structure types.
